### 2023-05-15 docs/minutes/slides_11_05/document.tex
restart canoncial 12 and noise

>>>>

	Lets proceed using this `Earth terms' model for now.

   So far we have been considering inference of only the GW terms $\bar{\theta}_{\rm GW}$. It is important to be able to infer the pulsar terms $\bar{\theta}_{\rm PSR}$.

   Lets try and include $f \, (t=0)$ and $\dot{f} \, (t=0)$ in our nested sampling.

   We have a uniform prior of $\pm 1 \%$ about the true value for these two parameters

\begin{frame}{Earth terms model $\bar{\theta}_{\rm GW}$ and $f \, (t=0)$, $\dot{f} \, (t=0)$}
	\includegraphics[width=0.9\textwidth,height=0.7\textwidth]{images/fprior_earth_corrected_result}
\end{frame}

### 2023-05-15 docs/minutes/slides_19_05/document.tex
restart canoncial 12 and noise

\date{EE/GW meeting, May 11, 2023}

@@

	\begin{itemize}
		\item \alert{Problem = overly narrow,biased posteriors from nested sampling}. Even for ``easy" systems!
	\end{itemize}

Here is an easy system: $h = 10^{-2}, \sigma_m = 10^{-13}, \sigma_p = 0.0$ \newline 
\centering
\includegraphics[width=0.5\textwidth,height=0.5\textwidth]{images/example_system}

\raggedright
If the true declination $\delta = 1.0$, NS might give us a posterior of $\sim 0.95$ but variance v.v. small and posterior does not capture true value

@@

@@

\begin{frame}{Earth terms model $\bar{\theta}_{\rm GW}$ and $f \, (t=0)$, $\dot{f} \, (t=0)$}
	\includegraphics[width=0.9\textwidth,height=0.7\textwidth]{images/fprior_earth_corrected_result}
\end{frame}

>>>>

\date{EE/GW meeting, May 19, 2023}

@@

		Last time: Problems at small $h$, nasty likelihood curves

@@

\begin{frame}
	Full NS search for \alert{all parameters} \newline 
	$\bar{\theta} = [\bar{\theta}_{\rm GW}, \, f, \, (t=0) \, \dot{f} \, (t=0) ]$ \newline 
	with $h = 10^{-10}$, $\sigma_m = 10^{-11}$ \newline 
	Note: pulsar distance is no longer part of model. $\gamma$ doesn't matter

\begin{frame}
		\includegraphics[width=0.9\textwidth,height=0.9\textwidth]{images/canonical_mixed_result}
\end{frame}

\begin{frame}
	\includegraphics[width=0.9\textwidth,height=0.9\textwidth]{images/canonical_mixed_f_result}
\end{frame}

\begin{frame}
	Next steps:
	\begin{itemize}
		\item Bayes factors vs. strain (currently running)
		\item Process noise $\sigma_p$
		\item Looser priors on $f$, $\dot{f}$? Do we need to?
		\item Can we add PSR terms back in? Do we need to?
	\end{itemize}
\end{frame}

\begin{frame}[standout]
	Fin.
\end{frame}

\appendix

\begin{frame}[fragile]{Backup slides}
	Sometimes, it is useful to add slides at the end of your presentation to
	refer to during audience questions.

	The best way to do this is to include the \verb|appendixnumberbeamer|
	package in your preamble and call \verb|\appendix| before your backup slides.

	\themename will automatically turn off slide numbering and progress bars for
	slides in the appendix.
\end{frame}

\begin{frame}[fragile]{Where did $\sigma_m$ value come from?}
The measurement noise is

$$ \sigma_m = f \frac{\sigma_{\rm TOA}}{\rm cadence}$$

So for a MSP ( $f \sim 100 Hz$) observed with a weekly cadence and $\sigma_{\rm TOA} \sim 1 \mu$s:

$$\sigma_m \sim 1.6 \times 10^{-10}$$

The very best pulsars might have $\sigma_{\rm TOA} \sim 10$ ns:

$$\sigma_m \sim 1.6 \times 10^{-12}$$
\end{frame}

\begin{frame}{$\gamma$ likelihood}
	\includegraphics[width=0.8\textwidth,height=0.8\textwidth]{images/likelihood_gamma_1}
\end{frame}

@@

\begin{frame}{Earth terms model $\bar{\theta}_{\rm GW}$ and $f \, (t=0)$, $\dot{f} \, (t=0)$}
	\includegraphics[width=0.9\textwidth,height=0.7\textwidth]{images/canonical_mixed_result}
\end{frame}
